Emulating Comparative Oncology Trials with Real-world Evidence Studies (ENCORE): Process Development and Methodological Considerations for Oncology Real-World Data

### 2025-07-06 manuscript/manuscript.qmd
updated word count

[**Manuscript word count:**]{.underline} 4,509 words / 8,000 words

[**Abstract word count:**]{.underline} 224 words / 250 words

@@

[***Proposed target journals:***]{.underline} *CPT =\> JCO CCI =\> ...*

>>>>

[**Manuscript word count:**]{.underline} 4,541 words / 8,000 words

[**Abstract word count:**]{.underline} 228 words / 250 words

@@
